Separating Use and Reuse to Improve Both

### 2017-05-23 FACS/Intro.tex
.

In essence we believe that a problem with the design of classes in
languages like Java is that classes
% do too many things at once. In particular they 
act both as units of \emph{use} and \emph{reuse}.
That is, in languages like Java, class names can be \emph{use}d as
type and instantiated.  Classes can also be subclassed to provide
\emph{reuse} of code.

>>>>

In essence we believe that a problem with the design of classes in
languages like Java is that classes
do too many things at once. In particular they 
act both as units of \emph{use} and \emph{reuse}:
 classes can be \emph{use}d as
type and instantiated; classes can also be subclassed to provide
\emph{reuse} of code.
